Astrophysical calibration of gravitational-wave detectors

### 2015-07-21 docs/cosmic_cal.tex
Added a posterior probability figure and ended a line mid-sentence!

For each of the simulated sources we have used the {\tt emcee} python MCMC package to perform 
parameter estimation over the unknown source parameters using the prior as discussed in 
Section~\ref{sec:priors}. In each case we use an estimate of the noise PSD based on the design 
sensitivity, but simulated as if estimated by averaging 64 separate PSD estimates and scaled with 
the same factor as applied to the injection and noise\footnote{We do not account for there being 
a difference between the estimated PSD and the actual PSD of the analysed section of data. This 
difference would be very much correlated with the scale factor, so in reality our estimate of the 
scale factor would be a combination of the calibration offset and the difference in the PSD. As 
such our results on real data would be an upper limit on the calibration scale factor.}. This has 
provided posterior probability distributions on the calibration scale factors for each detector 
\MP{Show an example for both source types}. From these we have calculated the 68\% credible region 
on the scale factors for each detector (if these were Gaussian distributions this is equivalent to 
the region bounded by $1\sigma$ intervals). For all the signals at each distance increment we have 
produced the distribution of the fractional half widths (i.e.\ $1\sigma$) of these scale factors 
confidence intervals compared to the actual value. These are shown as boxplots in 
figures~\ref{fig:bnsresults} and \ref{fig:nsbhresults} for the \ac{BNS} and \ac{NSBH} systems 
respectively. The boxes show the extent from the lower to upper quartile of the values, whilst the 
whiskers represent range of values. The black line within each box gives the median value and the 
star gives the mean value. Also shown on each plot as the dashed magenta line is the percentage of 
proposed injections that actually fulfilled the detection criterion.

>>>>

For each of the simulated sources we have used the {\tt emcee} python MCMC package to perform 
parameter estimation over the unknown source parameters using the prior as discussed in 
Section~\ref{sec:priors}. In each case we use an estimate of the noise PSD based on the design 
sensitivity, but simulated as if estimated by averaging 64 separate PSD estimates and scaled with 
the same factor as applied to the injection and noise\footnote{We do not account for there being 
a difference between the estimated PSD and the actual PSD of the analysed section of data. This 
difference would be very much correlated with the scale factor, so in reality our estimate of the 
scale factor would be a combination of the calibration offset and the difference in the PSD. As 
such our results on real data would be an upper limit on the calibration scale factor.}. This has 
provided posterior probability distributions on the calibration scale factors for each detector 
\MP{Show an example for both source types}. An example of the marginalised posterior probablil From 
these we have calculated the 68\% credible region 
on the scale factors for each detector (if these were Gaussian distributions this is equivalent to 
the region bounded by $1\sigma$ intervals). For all the signals at each distance increment we have 
produced the distribution of the fractional half widths (i.e.\ $1\sigma$) of these scale factors 
confidence intervals compared to the actual value. These are shown as boxplots in 
figures~\ref{fig:bnsresults} and \ref{fig:nsbhresults} for the \ac{BNS} and \ac{NSBH} systems 
respectively. The boxes show the extent from the lower to upper quartile of the values, whilst the 
whiskers represent range of values. The black line within each box gives the median value and the 
star gives the mean value. Also shown on each plot as the dashed magenta line is the percentage of 
proposed injections that actually fulfilled the detection criterion.

\begin{figure}
 \begin{center}
  \includegraphics[width=1.0\textwidth]{bns_post_fig.pdf}
 \end{center}
 \caption{\label{fig:bnspost} The marginalised posterior probability distributions for the unknown
 parameters of a \ac{BNS} system including calibration scaling factors for the three detectors (H1, 
L1 and V1). The injected signal had \ac{SNR} of 8.7, 10.9 and 4.1 and percentage uncertainties in 
the calibration scale factors of 14\%, 11\% and 27\% for each of the detectors respectively.}
\end{figure}
